Between-dataset comparisons

### 2019-11-14 analysis/reports/cross_dataset.Rmd
just get the csv
run more fia

---
title: "Between-dataset comparisons"
output: 
  github_document
---

@@

@@

@@

@@

>>>>

---
title: "Between-dataset comparisons"
output: 
  github_document
params:
  on_hpg: [FALSE]
---

@@

if(params$on_hpg) {

@@

write.csv(all_di, "all_di.csv", row.names = F)
} else {
  all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)
}
```

@@

dat_skew_nsamples <- skew_nsamples +
  facet_wrap(vars(dat))

dat_skew_nsamples

@@

```{r histograms, fig.height = 6, fig.width =6}

skewhists <- ggplot(data = all_di, aes(x = skew_percentile)) +
  geom_histogram(binwidth = 5, alpha = .3) +
  geom_histogram(binwidth = 5, data = filter(all_di, nsamples == 2500)) +
  theme_bw() +
  facet_grid(rows = vars(dat), cols = vars(singletons), scales = "free_y") +
  ggtitle("Skewness")
skewhists

simpsonhists <- ggplot(data = all_di, aes(x = simpson_percentile)) +
  geom_histogram(binwidth = 5, alpha = .3) +
  geom_histogram(binwidth = 5, data = filter(all_di, nsamples == 2500)) +
  theme_bw() +
  facet_grid(rows = vars(dat), cols = vars(singletons), scales = "free_y") +
  ggtitle("Simpson")
simpsonhists
